Nodal Discontinuous Galerkin Method for the Euler Equations of Fluid Dynamics

### 2017-07-18 Documents/Euler/dgEulerCurvilinear.tex
Added skeleton convergence table

@@

@@

>>>>

\subsubsection{Entropy Waves (Accuracy Test)}

\begin{table}
  \begin{center}
  \caption{$L^{\infty}$ error and convergence rates for the entropy wave problem.}
  \label{tab:streamingSineWave}
  \begin{tabular}{ccccccccc}
    & \multicolumn{4}{c}{SSP-RK2} & \multicolumn{4}{c}{SSP-RK3} \\
    \cmidrule(r){2-5} \cmidrule(r){6-9}
    $N$ & DG(1) & Rate & DG(2) & Rate & DG(2) & Rate & DG(3) & Rate \\
    \midrule \midrule
    8     & $x.xxx\times10^{-x}$ & ---  & $x.xxx\times10^{-x}$ & ---  & $x.xxx\times10^{-x}$ & ---  & $x.xxx\times10^{-x}$  & --- \\
    16   & $x.xxx\times10^{-x}$ &x.xx& $x.xxx\times10^{-x}$ &x.xx& $x.xxx\times10^{-x}$ &x.xx& $x.xxx\times10^{-x}$ &x.xx \\
    32   & $x.xxx\times10^{-x}$ &x.xx& $x.xxx\times10^{-x}$ &x.xx& $x.xxx\times10^{-x}$ &x.xx& $x.xxx\times10^{-x}$ &x.xx \\
    64   & $x.xxx\times10^{-x}$ &x.xx& $x.xxx\times10^{-x}$ &x.xx& $x.xxx\times10^{-x}$ &x.xx& $x.xxx\times10^{-x}$ &x.xx \\
    128 & $x.xxx\times10^{-x}$ &x.xx& $x.xxx\times10^{-x}$ &x.xx& $x.xxx\times10^{-x}$ &x.xx& $x.xxx\times10^{-x}$ &x.xx \\
    256 & $x.xxx\times10^{-x}$ &x.xx& $x.xxx\times10^{-x}$ &x.xx& $x.xxx\times10^{-x}$ &x.xx& $x.xxx\times10^{-x}$ &x.xx \\
    \midrule \midrule
  \end{tabular}
  \end{center}
\end{table}

\subsubsection{Sound Waves}

@@

\subsubsection{Shock Tube}

@@

\subsubsection{Homologous Collapse}
